Comparing Different Planned Missingness Designs in Longitudinal Studies

### 2018-06-10 Documentation/manuscript.Rnw
Manuscript
Common legend for illustration!!!

<<warning=FALSE,echo=FALSE>>=
cols <- c("Missing" = "red", "Observed" = "skyblue3")
splitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")

@@

<<warning=FALSE,echo=FALSE>>=
cols <- c("Missing" = "red", "Observed" = "skyblue3")
alternatesplitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")

@@

<<echo=FALSE>>=
cols <- c("Missing" = "red", "Observed" = "skyblue3")
waveplot <-  ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
@

<<echo=FALSE>>=
grid_arrange_shared_legend <- function(...) {
    plots <- list(...)
    g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
    lheight <- sum(legend$height)
    grid.arrange(
        do.call(arrangeGrob, lapply(plots, function(x)
            x + theme(legend.position="none"))),
        legend,
        ncol = 1,
        heights = unit.c(unit(1, "npc") - lheight, lheight))
}
@

@@

<<formillustration, fig.cap = "Low missingness", echo = FALSE, message = FALSE, warning = FALSE, fig.keep = TRUE, fig.pos = "H">>=
require(gridExtra)
require(grid)
require(ggplot2)

@@

grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
@

@@

<<echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=
sampsize
@

>>>>

<<warning=FALSE,echo=FALSE>>=
cols <- c("Missing" = "red", "Observed" = "skyblue3")
splitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.title.x = element_blank(),panel.background = element_rect(fill = NA)) + labs(y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")

@@

<<warning=FALSE,echo=FALSE>>=
cols <- c("Missing" = "red", "Observed" = "skyblue3")
alternatesplitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.title.y = element_blank(), axis.title.x = element_blank(),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")

@@

<<echo=FALSE>>=
cols <- c("Missing" = "red", "Observed" = "skyblue3")
waveplot <-  ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.title.x = element_blank(), axis.title.y = element_blank(),panel.background = element_rect(fill = NA)) + labs(fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
@

@@

<<formillustration, fig.cap = "Low missingness", echo = FALSE, message = FALSE, warning = FALSE, fig.keep = TRUE, fig.pos = "H">>=
require(gridExtra)
require(grid)
require(ggplot2)
require(lemon)

@@

#plots <- grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3, bottom=textGrob("x axis title", gp=gpar(fontsize=22)))

#grid_arrange_shared_legend(plots,position="bottom")

gg <- grid_arrange_shared_legend(splitplot, alternatesplitplot, waveplot, ncol=3, position="top")
grid.arrange(gg,bottom=textGrob("Questions Asked"))
#grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
@

@@

<<echo = FALSE, message = FALSE, warning = FALSE, warning=FALSE>>=X
sampsize
@
